Thermodynamic fragments for magic states in quantum computation

### 2021-02-24 magic_paper.tex
Tidied up before the mana section

\section{Introduction}
\label{sec:intro}

\begin{enumerate}
    \item Fault-tolerance~\cite{cit:raussendorf, cit:gross2, cit:markov, cit:gross, cit:nest, cit:nest2, cit:vidal, cit:fujii, cit:gottesman}
    \item Magic~\cite{cit:veitch, cit:veitch2, cit:wang, cit:wang2, cit:howard, cit:campbell, cit:gross3, cit:gross4}
    \item Bringing in majorization~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
    \item Section breakdown
\end{enumerate}

\section{Magic Resource Theories}
\label{sec:magic}

\subsection{Introduction}

@@

\subsection{Previous work}\label{sec:prev}

@@

\ddd{Things we MUST emphasize:
\begin{enumerate}
\item Perhaps a nice lead-in question: ``What happens if we view stabilizer states as thermodynamic equilibrium states and magic as a form of free energy?''
\item We have found a scenario in which it is impossible to describe a thermodynamic structure using any entropic approach!
\item We can tackle more `physicsy' questions like: how much magic can be distilled via available operations with some given fixed-point structure? 
\item This allows a diagnostic on the kind of operations needed to do good distillation. I.e. what fixed point structure should they have?
\item We go beyond the concept of monotones and replace a monotone with a $\sigma$-fragment.
\item We can get both upper and lower bounds on magic distillation.
\end{enumerate}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section{Phase Space formalism}
\label{sec:ps}

@@

The generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators,
\begin{align}
    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
	Z \ket{k} &= \omega^k \ket{k}, \label{eq:zpauli}
\end{align}
where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$. The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d \coloneqq \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
\begin{equation}\label{eq:ddef}
    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ (x, p) \in \cal{P}_d.
\end{equation}
The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
For a composite system with Hilbert space, $\hd = \hd[d_1] \otimes \dots \otimes \hd[d_n]$, the displacement operators are defined as
\begin{equation}\label{eq:composited}
    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
\end{equation}
where 
\begin{align*}
	\bmx \coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n},
\end{align*}
denotes the phase space point for an $n$--copy system.

@@

\subsection{Wigner representations for quantum states and quantum channels}\label{sec:wigner}

@@

The single-qudit Hadamard gate $H$ and phase gate $S$ generate the $d$-dimensional Clifford group $\cal{C}_d$~\cite{cit:gottesman1998}.
Their Wigner distributions are given by permutation matrices,
\begin{align}
    H &\coloneqq \frac{1}{\sqrt{d}}\sum_{j,k} \omega^{jk} \ketbra{j}{k}, \W[\bmy|\bmx]{H} = \delta_{y_0, -x_1}\delta_{y_1, x_0};\label{eq:H}\\
    S &\coloneqq \sum_k \tau^{k(k+1)} \ketbra{k}{k}, \W[\bmy|\bmx]{S} = \delta_{y_0, x_0}\delta_{y_1, x_0 + x_1 + 2^{-1}}.\label{eq:S}
\end{align}
\nick{Remove above paragraph?}

@@

\begin{theorem}
    Let $\R = (\F, \O)$ be a theory of magic.
    Every operation in $\O$ leaves at least one free state invariant,
  \begin{equation}
\O = \bigcup\limits_{\sigma \in \F} \O_\sigma.
\end{equation}
Therefore, $\rho \longrightarrow \tau$ in $\R$ if and only if $\rho \longrightarrow \tau$ in a $\sigma$--fragment of $\R$.
\end{theorem}
\begin{proof}
    Suppose $\E$ is in a $\sigma$--fragment $\O_\sigma$.
    Then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.

@@

The subdivision of magic theories into $\sigma$--fragments is powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in~\cref{sec:major}.

\subsection{Majorization of quasi-probabilities in $\sigma$--fragments}\label{sec:major}

In any magic theory, we can pick a certain free state, for example a stabilizer and view it as the analog of some thermal state $\gamma_\beta$.
Without loss of generality we can always write a state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z} e^{-\beta H}$ for some $\beta \ge 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
It then defines a set of free operations $\O_\sigma$ analogous to the thermal operations that preserve $\gamma_\beta$ the pre-order $\prec_{\R_\sigma}$ between these operations follows the rules of $\bmd$-majorization.

In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.

\begin{theorem}\label{thm:sigmamajor}
    Let $\R = (\F, \O)$ be a theory of magic. If $\rho \longrightarrow \tau$  in $\R$ then  $\W{\tau} \prec_\sigma \W{\rho}$ within at least one $\sigma$--fragment.
\end{theorem}
\begin{proof}
Suppose we can convert $\rho$ into $\tau$ in the magic theory. 
Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. 
Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
Since $\sigma$ is \nick{full-rank} and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.
\end{proof}
This result can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
The physical difference between the two expressions is that the majorization ordering occurs in a specific $\sigma$-fragment.
Therefore, majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.

This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
\nick{This is more involved and we discuss this later in the paper.}

\nick{Also mention relative majorization somewhere}

\subsection{Majorization computations in $\sigma$--fragments}
The pre-order imposed by $\bmd$-majorization admits a numerically efficient reformulation in terms of Lorenz curves.
Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\tilde{\bmz} \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.

A vector $\bmy$ is said to \emph{$\bmd$--majorize} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
\begin{theorem}\label{thm:dmajor}
    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
\end{theorem}
A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.
An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{Recast in terms of magic - replace with~\cref{fig:test}?}
    }
    \label{fig:lctoy}
\end{figure}

It is now straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.

We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
\begin{proposition}\label{thm:lccont}
	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$. 
	\nick{In the sense that if $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
	I think this clears up the narrative quite a bit? - Should we keep and prove this result?} \ddd{[Is a nice result...hmm let's wait and see. It might distract from the main message.]}
\end{proposition}
The proof of this important result is in \nick{the appendix}.
The consequence of this statement is that infinitesimal changes in state $\sigma$ only result in infinitesimal shifts of the $\sigma$--fragment.
Therefore, Lorenz curves and majorization analysis in general \nick{behave nicely in the presence of / are robust under} imperfections in the experimental implementation of quantum operations.
In particular, any $\sigma_0$--fragment defined by a non full-rank state $\sigma_0$ can be approximated by a $\sigma$--fragment defined by a full-rank $\sigma$ which is arbitrarily close to $\sigma_0$, such that $\sigma = (1-\epsilon)\sigma_0 + \epsilon\frac{1}{d}\id$, for some small $\epsilon > 0$.
Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.
For simplicity, we restrict analysis to $\sigma$-fragments, where $\sigma$ is full-rank.

Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
As a consequence, checking whether a state conversion $\rho \longrightarrow \tau$ is possible as per~\cref{thm:dmajor}, reduces to the condition $\lc{\rho}{\sigma}(x) \leq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.

The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
The exact form of the monotone is given in~\cref{app:areamono}

\ddd{[relate to mana?]} \nick{the area depends on several positive Wigner components and cannot be written as a function of mana annoyingly - should we include the area? Have a look at~\cref{app:areamono}}

@@

\section{Magic state interconversion and Lorenz curve comparison}
\label{sec:distill}

Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
As a simple example, the dephasing channel
\begin{equation}\label{eq:dephase}
	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{k}{k}\rho\ketbra{k}{k}
\end{equation}
removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$.

Lorenz curves provide an efficient method of numerically checking if a certain state conversion is impossible within a $\sigma$--fragment by exploiting the equivalence with $d$--majorization stated in~\cref{thm:dmajor}.
Such methods are often more conclusive than magic monotones as we discuss in section~\cref{sec:scmana}.

\subsection{Majorization in magic theories}\label{sec:scmana}
We now discuss majorization features common to all fragments, before specialising to particular $\sigma$--fragments and how analysis in them proceeds.

As discussed above, we know that every magic interconversion problem can be analysed across all $\sigma$--fragments that reflect symmetries of the circuit and moreover the pre-order in each such fragment is exactly specified by $d$--majorization.

Consider a general magic state interconversion in $\O_\sigma$, 
\begin{equation}
	\rho \xrightarrow{\E \in \O_\sigma} \tau.
\end{equation}

Magic theories utilise monotone bounds of the form
\begin{equation}\label{eq:majbound}
    \M(\rho) \geq \M(\tau),
\end{equation}
to determine whether the interconversion is allowed.
Monotone bounds hold independently of $\sigma$--fragments, therefore they provide no understanding with regard to the type of operations that allow the interconversion.

New bounds can be obtained in the $\sigma$--fragment by pointwise Lorenz curve comparison of the initial and target states,
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
\end{equation}
This inequality is parametrised by $x$ and if it is not satisfied at any point $x$, then the Lorenz curves intersect and the conversion is impossible.
We can refine the independent constraints stemming from this inequality and consider it at only the locations of the target state elbows.
\begin{theorem}\label{thm:elbows}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.

	Let $n'$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_n'\}$ be their locations.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,n'$.
\end{theorem}
A proof is provided in~\cref{app:lc_constraints}.
Any of the $t$ inequalities in the theorem provides a valid contraint leading to some upper distillation bound, and the more one cosiders, the stricter the bound is.

\nick{We can skip mana and just discuss sum-negativity}

One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state \nick{CITE}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln{(2\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity} ($\rm{sn}$) \nick{CITE} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}
Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical is distillation settings.} magic monotone, so it provides a necessary condition for magic state interconvertibility.

Here, we show that its properties can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
In fact, our current setting makes it apparent that the mana provides a weaker condition than majorization for all magic state interconversions.

>>>>

\section{Introduction and background}
\label{sec:intro_prev}

\begin{enumerate}
    \item Fault-tolerance~\cite{cit:raussendorf, cit:gross2, cit:markov, cit:gross, cit:nest, cit:nest2, cit:vidal, cit:fujii, cit:gottesman}
    \item Magic~\cite{cit:veitch, cit:veitch2, cit:wang, cit:wang2, cit:howard, cit:campbell, cit:gross3, cit:gross4}
    \item Bringing in majorization~\cite{cit:cwiklinski, cit:lostaglio2, cit:lostaglio, cit:gour, cit:janzing, cit:brandao2, cit:gour2, cit:marshall, cit:nielsen}
\end{enumerate}

\subsection{Introduction}
\label{sec:intro}

@@

\subsection{Previous work}
\label{sec:prev}

@@

\ddd{Things we MUST emphasize:
\begin{enumerate}
\item Perhaps a nice lead-in question: ``What happens if we view stabilizer states as thermodynamic equilibrium states and magic as a form of free energy?''
\item We have found a scenario in which it is impossible to describe a thermodynamic structure using any entropic approach!
\item We can tackle more `physicsy' questions like: how much magic can be distilled via available operations with some given fixed-point structure? 
\item This allows a diagnostic on the kind of operations needed to do good distillation. I.e. what fixed point structure should they have?
\item We go beyond the concept of monotones and replace a monotone with a $\sigma$--fragment.
\item We can get both upper and lower bounds on magic distillation.
\end{enumerate}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\section{Preliminaries and definitions}
\label{sec:ps}

@@

The generalised Pauli matrices $X, Z$ can be defined by their respective roles as shift and phase operators,
\begin{align}
    X \ket{k} &= \ket{k + 1} \label{eq:xpauli}\\
	Z \ket{k} &= \omega^k \ket{k}, \label{eq:zpauli}
\end{align}
where $\omega \coloneqq e^{2\pi i/d}$ is the $d$-th root of unity and addition is modulo $d$. The Hilbert space $\hd$ is associated with a phase space $\cal{P}_d = \mathbb{Z}_d \times \mathbb{Z}_d$, where every point $\bmx \coloneqq (x, p)$ corresponds to a displacement operator, defined as
\begin{equation}\label{eq:ddef}
    D_{\bmx} \coloneqq \tau^{x p} X^{x} Z^{p},\ (x, p) \in \cal{P}_d.
\end{equation}
The phase factor $\tau \coloneqq -\omega^{1/2}$ ensures unitarity.
For a composite system with product dimension $d = d_1 \dots d_n$ and Hilbert space, $\hd = \hd[d_1] \otimes \dots \otimes \hd[d_n]$, the displacement operators are defined as
\begin{equation}\label{eq:composited}
    D_{\bmx} \coloneqq D_{(x_1, p_1)} \otimes \dots \otimes D_{(x_n, p_n)},
\end{equation}
where 
\begin{align*}
	\bmx \coloneqq (x_1, p_1, x_2, p_2, \dots, x_n, p_n) \in \cal{P}_{d_1} \times \dots \times \cal{P}_{d_n} \eqqcolon  \cal{P}_d,
\end{align*}
denotes the phase space point for an $n$--copy system.

@@

\subsection{Wigner representations for quantum states and quantum operations}\label{sec:wigner}

@@

\subsection{Magic monotones}
\label{sec:mono}

We highlight the defining property of a monotone, as it is useful in later discussion.
\begin{definition}[\textbf{Resource monotone}]\label{def:mono}
    Let $\R = (\F, \O)$ be a resource theory.
    A resource monotone $\M$ is a projection from the set of quantum states of the theory onto the real line, so that $\M$ is monotonically decreasing under free operations,
    \begin{equation}
        \M(\rho_1) \leq \M(\rho_2)\ \text{whenever}\ \rho_1 \prec_{\R} \rho_2.
    \end{equation}
\end{definition}

\nick{We can skip mana and just discuss sum-negativity}
One of the most fundamental and commonly used magic monotones is the \emph{mana} of a state~\cite{cit:veitch2}, defined as
\begin{equation}
    \mana{\rho} \coloneqq \ln{(2\hspace{1pt}\sn{\rho}+1)},
\end{equation}
where the \emph{sum-negativity} ($\rm{sn}$)~\cite{cit:veitch2} is the sum of the negative components in $\W{\rho}$,
\begin{equation}
    \sn{\rho} \coloneqq \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}}.
\end{equation}
Mana is an additive\footnote{It satisfies the condition $\mana{\rho_1 \otimes \rho_2} = \mana{\rho_1} + \mana{\rho_2}$ which is practical in distillation settings.} magic monotone, so it provides an analytical necessary condition for many-copy magic state interconvertibility.

\subsection{Majorization}
\label{sec:major}

The pre-order imposed by $\bmd$-majorization admits a numerically efficient reformulation in terms of Lorenz curves.
Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\tilde{\bmz} \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.

A vector $\bmy$ is said to \emph{$\bmd$--majorize} another vector $\bmx$ if and only if the Lorenz curve $\lc{\bmy}{\bmd}$ lies above Lorenz curve $\lc{\bmx}{\bmd}$, thus reducing $\bmd$--majorization into a finite set of inequalities.
\begin{theorem}\label{thm:dmajor}
    Let $\bmx, \bmy, \bmd \in \reals^d$, such that the components of $\bmd$ are positive. 
    Then, $\bmx \prec_{\bmd} \bmy$ if and only if $\lc{\bmx}{\bmd}(x) \leq \lc{\bmy}{\bmd}(x)$ for all $x \in [0,1]$ with strict equality at $x=1$.
\end{theorem}
A restatement of the theorem including more equivalent conditions and a proof are provided in~\cref{app:major}.

@@

\begin{theorem}\label{thm:frag}
    Let $\R = (\F, \O)$ be a theory of magic.
    Every operation in $\O$ leaves at least one free state invariant,
  \begin{equation}
\O = \bigcup\limits_{\sigma \in \F} \O_\sigma.
\end{equation}
Therefore, $\rho \longrightarrow \tau$ in $\R$ if and only if $\rho \longrightarrow \tau$ in a $\sigma$--fragment of $\R$.
\end{theorem}
\begin{proof}
    Suppose $\E$ is in a $\sigma$--fragment $\O_\sigma$.
    Then it is also in $\O$, hence $\bigcup\limits_{\sigma \in \F} \O_\sigma \subseteq \O$.

@@

Every  quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$--fragments that reflect these symmetries.
As a simple example, the dephasing channel
\begin{equation}\label{eq:dephase}
	\Delta(\rho) = \sum_{k \in \mathbb{Z}_d} \ketbra{k}{k}\rho\ketbra{k}{k}
\end{equation}
removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
A noise channel consisting only of such dephasing operations can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$. \nick{Have proven in appendix that we need to consider \emph{only} the pure stabilizer fragments - not mixed ones}

The subdivision of magic theories into $\sigma$--fragments is also powerful because the pre-order $\prec_{\R_\sigma}$ of every $\sigma$--fragment is described by well-behaved majorization tools, as we establish in the rest of this section.

\subsection{Majorization of quasi-probabilities in $\sigma$--fragments}\label{sec:major_frag}

We can approach any magic theory through a thermodynamic lens, and in doing so we are provided with valuable insights on the structure of the theory. 
Firstly, any free state, for example a stabilizer state, can be viewed as a thermal state $\gamma_\beta$.
Without loss of generality we can always write a quantum state $\sigma$ as a thermal state, $\sigma = \gamma_\beta \coloneqq \frac{1}{\Z_\beta} e^{-\beta H}$ for some $\beta \geq 0$ and Hamiltonian $H$ (either effective or actual)\footnote{Technicalities arise for the case where $\sigma$ is not full rank, but this can be still described via $ \beta \rightarrow 0$ limiting process.}.
We can also view the set of free operations $\O_\sigma$ as a counterpart of thermal operations, in the sense that any operation $\E$ in $\O_\sigma$ preserves state $\sigma$.

It is then apparent that the pre-order $\prec_{\R_\sigma}$ between the operations in the $\sigma$--fragment follows the rules of $\bmd$-majorization as outlined in~\cref{sec:major}.
In particular, the pre-order $\prec_{\R_\sigma}$ of the $\sigma$--fragment $\R_\sigma = (\F, \O_\sigma)$ between $d$-dimensional states corresponds to the majorization pre-order $\prec_{\W{\sigma}}$ between their $d^2$-dimensional Wigner distributions.
For simplicity we shall merge the notation into $\prec_\sigma$, as there is little risk of confusion.

Note that the Wigner components of an $n$-copy state $\rho^{\otimes n}$ can be calculated directly from $\W{\rho}$ by convolution of the distribution with itself,
\begin{equation}
	\W{\rho^{\otimes n}} = \rm{W}_{\rho}^{\otimes n},
\end{equation}
where $\otimes$ can be interpreted as the usual Kroenecker product in the last expression.

Furthermore, we restrict our analysis to $\sigma$--fragments, where $\sigma$ is full-rank.
This is justified as majorization is continuous between fragments, in the sense that the pre-orders $\prec_\sigma$ and $\prec_{\sigma'}$ are equivalent for states $\sigma$ and $\sigma'$ which are $\epsilon$-close. \nick{CHECK}
Therefore, majorization analysis is robust under imperfections in the experimental implementation of quantum operations.

In particular, any $\sigma$--fragment, with $\sigma$ not full-rank, can be approximated by the $\sigma'$--fragment defined as a mixture of $\sigma$ with uniform noise, $\sigma' = (1-\epsilon)\sigma + \epsilon\frac{1}{d}\id$, for some infinitesimal $\epsilon > 0$, so that $\sigma'$ is full-rank and arbitrarily close to $\sigma$.
There exist many $\sigma$--fragments with $\sigma$ not full-rank, such as when $\sigma$ is a pure stabilizer, e.g. the zero state as depicted in~\cref{fig:zero}. 
Operations in such fragments include important stabilizer operations like the replacement channel defined as $\E(\rho) = \sigma$ for all states $\rho$.

\begin{theorem}\label{thm:sigmamajor}
    Let $\R = (\F, \O)$ be a theory of magic. If $\rho \longrightarrow \tau$  in $\R$ then  $\W{\tau} \prec_\sigma \W{\rho}$ within at least one $\sigma$--fragment.
\end{theorem}
\begin{proof}
Suppose we can convert $\rho$ into $\tau$ in the magic theory. 
Thus there is some $\O_\sigma$ and some $\E \in \O_\sigma$ such that $\E(\rho) = \tau$, and $\E(\sigma)=\sigma$. 
Therefore, the Wigner distribution of this free operation satisfies $\W{\E} \in \stochw$ and $\W{\E}\W{\rho} = \W{\tau}$. 
Since $\sigma$ is full-rank and free, its Wigner distribution is strictly positive in all components, so it directly follows from~\cref{def:dmajor} that $\W{\tau} \prec_{\sigma} \W{\rho}$.

\nick{The theorem statement and proof currently assume that $\sigma$ is full-rank}
\end{proof}

The result of~\cref{thm:sigmamajor} can be understood as an extension of the idea of a magic monotone, where we replace $\M(\tau) \leq \M(\rho)$ with $\W{\tau} \prec_\sigma \W{\rho}$. 
The physical difference between the two expressions is that the majorization ordering occurs in a specific $\sigma$--fragment.
Therefore, majorization constraints can be used to place upper bounds on magic state distillation in a way that allows one to incorporate the physics of the allowed operations -- specifically, it enables us to bound how much magic can be distilled via quantum operations that, for example, preserve the equilibrium state of the system, or via operations that are symmetric about the $Z$-axis of the Bloch sphere.
We discuss distillation upper bounds in~\nick{REF}

This approach can also provide \emph{lower bounds} on distillation, however now more structure about the specific free operations must be included. 
We discuss distillation lower bounds in~\nick{REF}

\nick{Mention relative majorization as a possibility}

\subsection{Majorization computations in $\sigma$--fragments}

It is straightforward to construct Lorenz curves for Wigner distributions in any $\sigma$--fragment.
As we have seen in~\cref{thm:sigmamajor}, for any full-rank free state $\sigma$ we have that $\W{\sigma}$ is a strictly positive full-rank probability distribution, and so one can define a corresponding notion of $d$--majorization on \emph{quasi}--distributions.
We write $\lc{\rho}{\sigma}(x)$ for the Lorenz curve of $\W{\rho}$ with respect to $\W{\sigma}$.

An example of comparison between different Lorenz curves is illustrated in~\cref{fig:lctoy}.
The curves in the figure are constructed in the \emph{unital fragment}, i.e. the $\sigma$--fragment defined by the maximally mixed state $\sigma = \frac{1}{d}\id$.
In~\cref{fig:lcs}, we illustrate the Lorenz curves of pure and noisy $n$-copy Strange states for $n$ up to $4$ in different $\sigma$--fragments.
\begin{figure}
    \centering
    \includegraphics[height=5cm]{figs/lctoy.pdf}
    \caption{Example of different Lorenz curves for quasi-probability vectors under $\bmd$-majorization.
    Vectors $\bmy$ and $\bmd$ are simply probability distributions.
    The curve corresponding to vector $\bmd$ is always the line segment connecting $(0,0)$ and $(1,1)$, so that any other Lorenz curve lies above it, for example $\bmx \prec_{\bmd} \bmd$.
    Curves $L_k(\bmx|\bmd)$ and $L_k(\bmy|\bmd)$ intersect, so $\bmx \nprec_{\bmd} \bmy$ as well as $\bmy \nprec_{\bmd} \bmx$.
    \nick{RECAST}
    }
    \label{fig:lctoy}
\end{figure}
\begin{figure}%
    \centering
    \subfigure[][]{%
    \label{fig:lcs_maxmix}%
    \includegraphics[height=3cm]{figs/lcs_maxmix.pdf}
    %\caption{Maximally mixed state $\frac{1}{3}\id$}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_thermal}%
    \includegraphics[height=3cm]{figs/lcs_thermal.pdf}
    %\caption{Zero state $\ketbra{0}{0}$}%
    }\\
    \subfigure[][]{%
    \label{fig:lcs_zero}%
    \includegraphics[height=3cm]{figs/lcs_zero.pdf}
    %\caption{Bound state}%
    }\hspace{1pt}%
    \subfigure[][]{%
    \label{fig:lcs_one}%
    \includegraphics[height=3cm]{figs/lcs_one.pdf}
    %\caption{Strange state $\ketbra{S}{S}$}%
    }
    \caption{\textbf{Lorenz curves of Strange state copies.} Lorenz curves of $\rho_{\rm{S}}n$ for $n=1,2,3,4$.
    Solid lines represent pure Strange states ($\epsilon = 0$); dashed lines represent noisy Strange states ($\epsilon = 0.1$).
    \subref{fig:lcs_maxmix} Unital fragment; \subref{fig:lcs_thermal} Thermal fragment with $H = (0,1,2)$ and $\beta = 0.5$; \subref{fig:lcs_zero} Fragment $\O_{\ketbra{0}{0}}$; \subref{fig:lcs_one} Fragment $\O_{\ketbra{1}{1}}$.    
    \nick{change / move / remove ?}
    }%
    \label{fig:lcs}
\end{figure}

We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.

Normalisation of the Wigner distribution \nick{REF} ensures that for all quantum states $\rho$, $\lc{\rho}{\sigma}(x) \geq 0$ and $\lc{\rho}{\sigma}(1) = 1$.
We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
As a consequence, checking whether a magic state conversion of the form
\begin{equation}
	\rho \xrightarrow{\E \in \O_\sigma} \tau
\end{equation} 
is possible, reduces to the set of constraints
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1],
\end{equation}
due to~\cref{thm:sigmamajor,thm:dmajor}.

We can refine the number of independent constraints stemming from this inequality. 
In fact, there are only as many independent constraints as there are elbows in the Lorenz curve of the target state as shown in~\cref{app:lc_constraints}.
However, in principle any one inequality defined at some location $x$ provides a valid constraint leading to some upper distillation bound, and the more locations one considers, the stricter the bound is.

The area $\A_\sigma(\rho)$ between the curve $L_{\rho|\sigma}$ and the line $y=1$ is a resource monotone in the $\sigma$--fragment. 
This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
The exact form of the monotone is given in~\cref{app:areamono}
\nick{should we include the area? Have a look at~\cref{app:areamono}}

@@

\section{Mana as a feature of majorization}

We now show that the magic monotone of mana, and equivalently the sum-negativity of a quantum state, can be viewed as majorization-based, and independent of the particular $\sigma$--fragment one works in.
In fact, our current setting makes it apparent that mana provides a weaker condition than majorization for all magic state interconversions.
